---
title: "Full documentation for: An alternative size variable for allometric investigations in subadults"
author: "Elaine Y. Chu"
date: "April 23, 2022"
output: 
  rmdformats::robobook:
    toc_float: false
---

```{r Global Chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, fig.width=8, fig.height=8, dpi=600)
```

# Overview
This research compendium provides code and steps needed to replicate the results of the publication: 

> Chu, E.Y., Stull, K.E., & Sylvester, A.D. (2022). An alternative size variable for allometric investigations in subadults. *In review.*

To run the code for this paper locally, please ensure that [R](https://cran.r-project.org/), and optionally [RStudio](https://www.rstudio.com/), are installed on the local system. 

Additionally, the following packages are used and should be installed using `install.packages("package_name")`:  

* [MVN](https://cran.r-project.org/web/packages/MVN/MVN.pdf)  
* [EnvStats](https://cran.r-project.org/web/packages/EnvStats/EnvStats.pdf)  
* [caret](https://topepo.github.io/caret/)  
* [lmodel2](https://cran.r-project.org/web/packages/lmodel2/lmodel2.pdf)  
* [tidyverse](https://www.tidyverse.org/)    
* [magrittr](https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html)  
* [gridExtra](https://cran.r-project.org/web/packages/gridExtra/vignettes/arrangeGrob.html)  

### How to cite
Please cite this compendium as:  

> Chu, E.Y., Stull, K.E., & Sylvester, A.D. (2022). Compendium of R code and data for *An alternative size variable for allometric investigations in subadults.* Accessed *Current Date*.

## The Data
All data are from the [Subadult Virtual Anthropology Database](https://zenodo.org/communities/svad). Specifically, this project uses portions of data from the [United States](https://zenodo.org/record/5193208#.YmWDqdrMKUk) and [South Africa](https://zenodo.org/record/3950301#.YmRaW9rMIdU), which are also directly provided in the **data** folder.

## Organization
This document is divided into three sections:  
1. [Data Manipulation](#munge)  
2. [Data Analysis](#analyze)  
3. [Data Visualization](#visualize)

## Setup
After the repository is on your local system, the following code is to setup your local R/RStudio enviornment:

```{r Setup, message=F}
rm(list=ls())  # clear global environment

if (!(grepl("subadult_sv_2022",getwd()))) {
  stop("Please set your working directory to 'subadult_sv_2022'.")
}

## Load required libraries
library(MVN)
library(caret)
library(lmodel2)
library(tidyverse)
library(gridExtra)

## Load personal ggplot2 theme
source("elaine_theme.R")
```

# Data Manipulation  {#munge}

## 1. Import data  

* Located in **data** folder  
* Stored as `.rds` files  

```{r Import Data}
us <- readRDS("data/us.rds")  # United States
za <- readRDS("data/za.rds")  # South Africa (Zuid-Afrika)
```

## 2. Calculate the geometric mean of long bone lengths  

* Geometric mean == "GM"  
* Long bone == "lb"  

```{r Calc GM, eval=F}
# U.S.
GM_len_us <- rep(NA, nrow(us))  # initialize empty vector for all us individuals
for(i in 1:nrow(us)){
  # extract lb lengths
  vars <- c(us[[i,"FDL"]],us[[i,"TDL"]],us[[i,"HDL"]],us[[i,"RDL"]])  
  # calculate GM using function from EnvStats
  GM_len_us[i] <- geoMean(vars)  
}

# Z.A.
GM_len_za <- rep(NA, nrow(za))  # initialize empty vector for all za individuals
for(i in 1:nrow(za)){
  # extract lb lengths
  vars <- c(za[[i,"FDL"]],za[[i,"TDL"]],za[[i,"HDL"]],za[[i,"RDL"]])  
  # calculate GM using function from EnvStats
  GM_len_za[i] <- geoMean(vars)  
}
```

## 3. Separate demographic and metric data 
```{r Separate demographic and metric data, eval=F}
# U.S.
demo_us <- us[1:4]  # demographic columns
metric_us <- cbind(us[5:ncol(us)],GM_len)  # metric columns, including GM_len

# Z.A.
demo_za <- za[1:4]  # demographic columns
metric_za <- cbind(za[5:ncol(za)],GM_len)  # metric columns, including GM_len
```

## 4. Combine demographic and logged metric data into a new data frame  

* Save as `*_log.rds` in **data** folder  

```{r Convert to log, eval=F}
# Combine columns, log metric data
us_log <- cbind(demo_us,log(metric_us))  
za_log <- cbind(demo_za,log(metric_za))  # combine columns, log metric data

# Save data
saveRDS(us_log,"data/us_log.rds")
saveRDS(za_log,"data/za_log.rds")
```

## 5. Set up for *k*-fold cross-validation with 10 folds  

* Set the seed for reproducibility  
* Save as `k_folds_list.rds`  

```{r k-fold, eval=F}
set.seed(2021)  # set seed for reproducibility

# k-Fold model construction using reduced (standard) major axis
k_folds <- createFolds(us_log$medrec, k=10)  # generate 10 folds

saveRDS(k_folds, "results/k_folds_list.rds")  # save
```


# Data Analysis  {#analyze}

## 1. Test for multivariate normality  {#Fig2}

**Mardia Test and Q-Q Plot:**

* Retain Q-Q Plot for **Figure 2**   

```{r Mardia, eval=F}
mvn(us[5:ncol(us)],mvnTest="mardia",covariance=TRUE,
    multivariatePlot="qq",showOutliers=TRUE)
```

**Henze-Zinkler Test:**

```{r HZ, eval=F}
mvn(us[5:ncol(us)],mvnTest="hz",covariance=TRUE,showOutliers=TRUE)
```

## 2. Kendall's Rank Correlation Coefficient

* Retain correlation values with stature as **Table 5**  
* Save all correlations as `variable_correlations.csv`    

```{r Kendall Tau, eval=F}
corr <- cor(us[5:ncol(us)], method="kendall")
corr[,1]  # correlation values with stature - Table 5
write.csv(corr,"results/variable_correlations.csv",row.names=FALSE)  # save
```

## 3. Reduced Major-Axis (RMA) Regression  

* Bivariate regression with *size variable ~ stature*  
* Storing each slope and intercept in the list `params`  
* Save as `rma_params_k_fold.rds`   

```{r RMA 1, eval=F}
for(c in 6:ncol(us_log)) {
  size_var <- colnames(us_log)[c]
  params[[size_var]] <- list()
  slope <- c()
  int <- c()
  
  for(kk in 1:length(k_folds)) {
    row_idx <- k_folds[[kk]]
    model <- suppressMessages(lmodel2(us_log[-row_idx,c] ~ 
                                        us_log[-row_idx,"stature"]))
    slope <- c(slope, model$regression.results$Slope[3])
    int <- c(int, model$regression.results$Intercept[3])
  }
  params[[size_var]]$slope <- slope
  params[[size_var]]$int <- int
}

saveRDS(params, "results/rma_params_k_fold.rds")  # save parameter list
```

## 4. Compile the contents of `params` into a data frame 

* Each row is the potential size variable, with mean slope and intercept as the two columns  
* Add a new row with distance of mean slope from 1 for each variable  
* Retain as **Table 5**  
* Save file as `rma_coefficients.csv`  

```{r RMA 2, eval=F}
# Initialize data frame with column `size_var` as each variable in `params`
rma_results <- data.frame(size_var=names(params))

for(v in 1:nrow(rma_results)) {
  rma_results$slope[v] <- mean(params[[v]]$slope)  # mean slope
  rma_results$intercept[v] <- mean(params[[v]]$int)  # mean intercept
}

length_idx <- which(rma_results$size_var %in% 
                      c("FDL","TDL","HDL","RDL"))  # identify lb lengths
rma_results <- rma_results[-length_idx,]  # remove lb lengths (n/a as size var)
rma_results$diff <- abs(1-rma_results$slope)  # calculate slope distance from 1
rownames(rma_results) <- NULL  # reset row numbers

write.csv(rma_results,"results/rma_coefficients.csv",row.names=FALSE)  # save
```

*In this step, RMSB, FMSB, and GM_msb are identified as having the closest slopes to 1 and are therefore retained for the rest of the analyses.*

## 5. Calculate allometry coefficients for each long bone length (**U.S. data**)

* Stature, RMSB, FMSB, GM_msb, GM_len  

```{r Allometry Coefs - U.S., eval=F}
## Allometric Coefficients - FDL
fdl_stature <- lmodel2(us_log[["FDL"]]~
                         us_log[["stature"]])$regression.results[3,]
fdl_rmsb <- lmodel2(us_log[["FDL"]]~
                      us_log[["RMSB"]])$regression.results[3,]
fdl_fmsb <- lmodel2(us_log[["FDL"]]~
                      us_log[["FMSB"]])$regression.results[3,]
fdl_gm_msb <- lmodel2(us_log[["FDL"]]~
                        us_log[["GM_msb"]])$regression.results[3,]
fdl_gm_len <- lmodel2(us_log[["FDL"]]~
                        us_log[["GM_len"]])$regression.results[3,]

## Allometric Coefficients - TDL
tdl_stature <- lmodel2(us_log[["TDL"]]~
                         us_log[["stature"]])$regression.results[3,]
tdl_rmsb <- lmodel2(us_log[["TDL"]]~
                      us_log[["RMSB"]])$regression.results[3,]
tdl_fmsb <- lmodel2(us_log[["TDL"]]~
                      us_log[["FMSB"]])$regression.results[3,]
tdl_gm_msb <- lmodel2(us_log[["TDL"]]~
                        us_log[["GM_msb"]])$regression.results[3,]
tdl_gm_len <- lmodel2(us_log[["TDL"]]~
                        us_log[["GM_len"]])$regression.results[3,]

## Allometric Coefficients - HDL
hdl_stature <- lmodel2(us_log[["HDL"]]~
                         us_log[["stature"]])$regression.results[3,]
hdl_rmsb <- lmodel2(us_log[["HDL"]]~
                      us_log[["RMSB"]])$regression.results[3,]
hdl_fmsb <- lmodel2(us_log[["HDL"]]~
                      us_log[["FMSB"]])$regression.results[3,]
hdl_gm_msb <- lmodel2(us_log[["HDL"]]~
                        us_log[["GM_msb"]])$regression.results[3,]
hdl_gm_len <- lmodel2(us_log[["HDL"]]~
                        us_log[["GM_len"]])$regression.results[3,]

## Allometric Coefficients - RDL
rdl_stature <- lmodel2(us_log[["RDL"]]~
                         us_log[["stature"]])$regression.results[3,]
rdl_rmsb <- lmodel2(us_log[["RDL"]]~
                      us_log[["RMSB"]])$regression.results[3,]
rdl_fmsb <- lmodel2(us_log[["RDL"]]~
                      us_log[["FMSB"]])$regression.results[3,]
rdl_gm_msb <- lmodel2(us_log[["RDL"]]~
                        us_log[["GM_msb"]])$regression.results[3,]
rdl_gm_len <- lmodel2(us_log[["RDL"]]~
                        us_log[["GM_len"]])$regression.results[3,]
```

## 6. Compile all allometry coefficients into a single data frame (**U.S. data**)  

* Save as `us_allometry_coefs.csv`  

```{r CompDF - U.S., eval=F}
long_bone <- c(rep("Humerus",5),rep("Radius",5),
               rep("Femur",5),rep("Tibia",5))
method <- rep(c("Stature","RMSB","FMSB","GM_Midshaft","GM_Length"),4)
slope <- c(hdl_stature$Slope,hdl_rmsb$Slope,hdl_fmsb$Slope,
           hdl_gm_msb$Slope,hdl_gm_len$Slope,
           rdl_stature$Slope,rdl_rmsb$Slope,rdl_fmsb$Slope,
           rdl_gm_msb$Slope,rdl_gm_len$Slope,
           fdl_stature$Slope,fdl_rmsb$Slope,fdl_fmsb$Slope,
           fdl_gm_msb$Slope,fdl_gm_len$Slope,
           tdl_stature$Slope,tdl_rmsb$Slope,tdl_fmsb$Slope,
           tdl_gm_msb$Slope,tdl_gm_len$Slope)
compDF <- data.frame(long_bone, method, slope)  # combine into compDf
compDF$slope <- as.numeric(as.character(compDF$slope))  # make numeric
compDF$long_bone <- factor(compDF$long_bone, 
                           levels=c("Humerus","Radius","Femur","Tibia"))
compDF$method <- factor(compDF$method, 
                        levels=c("Stature","RMSB","FMSB",
                                 "GM_Midshaft","GM_Length"))

write.csv(compDF,"results/us_allometry_coefs.csv",row.names=FALSE)  # save
```

## 7. Calculate allometry coefficients for each long bone length (**Z.A. data**)

* Stature, RMSB, FMSB, GM_msb, GM_len  

```{r Allometry Coefs - Z.A., eval=F}
## Allometric Coefficients - FDL
fdl_stature <- lmodel2(za_log[["FDL"]]~
                         za_log[["stature"]])$regression.results[3,]
fdl_rmsb <- lmodel2(za_log[["FDL"]]~
                      za_log[["RMSB"]])$regression.results[3,]
fdl_fmsb <- lmodel2(za_log[["FDL"]]~
                      za_log[["FMSB"]])$regression.results[3,]
fdl_gm_msb <- lmodel2(za_log[["FDL"]]~
                        za_log[["GM_msb"]])$regression.results[3,]
fdl_gm_len <- lmodel2(za_log[["FDL"]]~
                        za_log[["GM_len"]])$regression.results[3,]

## Allometric Coefficients - TDL
tdl_stature <- lmodel2(za_log[["TDL"]]~
                         za_log[["stature"]])$regression.results[3,]
tdl_rmsb <- lmodel2(za_log[["TDL"]]~
                      za_log[["RMSB"]])$regression.results[3,]
tdl_fmsb <- lmodel2(za_log[["TDL"]]~
                      za_log[["FMSB"]])$regression.results[3,]
tdl_gm_msb <- lmodel2(za_log[["TDL"]]~
                        za_log[["GM_msb"]])$regression.results[3,]
tdl_gm_len <- lmodel2(za_log[["TDL"]]~
                        za_log[["GM_len"]])$regression.results[3,]

## Allometric Coefficients - HDL
hdl_stature <- lmodel2(za_log[["HDL"]]~
                         za_log[["stature"]])$regression.results[3,]
hdl_rmsb <- lmodel2(za_log[["HDL"]]~
                      za_log[["RMSB"]])$regression.results[3,]
hdl_fmsb <- lmodel2(za_log[["HDL"]]~
                      za_log[["FMSB"]])$regression.results[3,]
hdl_gm_msb <- lmodel2(za_log[["HDL"]]~
                        za_log[["GM_msb"]])$regression.results[3,]
hdl_gm_len <- lmodel2(za_log[["HDL"]]~
                        za_log[["GM_len"]])$regression.results[3,]

## Allometric Coefficients - RDL
rdl_stature <- lmodel2(za_log[["RDL"]]~
                         za_log[["stature"]])$regression.results[3,]
rdl_rmsb <- lmodel2(za_log[["RDL"]]~
                      za_log[["RMSB"]])$regression.results[3,]
rdl_fmsb <- lmodel2(za_log[["RDL"]]~
                      za_log[["FMSB"]])$regression.results[3,]
rdl_gm_msb <- lmodel2(za_log[["RDL"]]~
                        za_log[["GM_msb"]])$regression.results[3,]
rdl_gm_len <- lmodel2(za_log[["RDL"]]~
                        za_log[["GM_len"]])$regression.results[3,]
```

## 8. Compile all allometry coefficients into a single data frame (**Z.A. data**)   

* Save as `za_allometry_coefs.csv`  

```{r CompDF - Z.A., eval=F}
long_bone <- c(rep("Humerus",5),rep("Radius",5),rep("Femur",5),rep("Tibia",5))
method <- rep(c("Stature","RMSB","FMSB","GM_Midshaft","GM_Length"),4)
slope <- c(hdl_stature$Slope,hdl_rmsb$Slope,hdl_fmsb$Slope,
           hdl_gm_msb$Slope,hdl_gm_len$Slope,
           rdl_stature$Slope,rdl_rmsb$Slope,rdl_fmsb$Slope,
           rdl_gm_msb$Slope,rdl_gm_len$Slope,
           fdl_stature$Slope,fdl_rmsb$Slope,fdl_fmsb$Slope,
           fdl_gm_msb$Slope,fdl_gm_len$Slope,
           tdl_stature$Slope,tdl_rmsb$Slope,tdl_fmsb$Slope,
           tdl_gm_msb$Slope,tdl_gm_len$Slope)

compDF <- data.frame(long_bone, method, slope)
compDF$slope <- as.numeric(as.character(compDF$slope))
compDF$long_bone <- factor(compDF$long_bone, 
                           levels=c("Humerus","Radius","Femur","Tibia"))
compDF$method <- factor(compDF$method, 
                        levels=c("Stature","RMSB","FMSB",
                                 "GM_Midshaft","GM_Length"))

write.csv(compDF,"results/za_allometry_coefs.csv",row.names=FALSE)  # save
```


# Data Visualization  {#visualize}

## Figure 1
**Caption:** Sample age distributions by country.

```{r Fig 1}
# Add location column and subset for medrec, agey, and location
us_sub <- us %>% mutate(location="U.S.") %>% select(medrec,agey,location)
za_sub <- za %>%mutate(location="Z.A.") %>% select(medrec,agey,location)

# Combine into full data frame
full_data <- rbind(us_sub, za_sub)

# Plot sample distribution as bar chart
ggplot(full_data, aes(x=as.integer(agey))) + 
  geom_bar(fill="grey75") + 
  elaine_theme + labs(x="Age (years)", y="Count") + 
  scale_x_continuous(breaks=0:12) + 
  geom_text(stat="count", aes(label=..count..), color="black") + 
  facet_grid(rows=vars(location), scale="free_y")
```

## Figure 2
**Caption:** Chi-square Q-Q plot to visualize multivariate normality. The solid black line represents multivariate normality, and the deviation of the pattern of filled circles indicates non-normality of the U.S. data.

*Figure generated when testing for [multivariate normality](#Fig2)*

## Figure 3
**Caption:** Inter-long bone allometric relationships. The solid red line across slope=1.0 represents isometry. Solid line = stature, dashed line = RMSB, dotted line = FMSB, dot-dash line = GM midshaft breadth, two-dash line = GM diaphyseal length.

```{r Fig3, fig.width=8, fig.height=4}
## Import allometry coefficient data
us_coef <- read.csv("results/us_allometry_coefs.csv")
za_coef <- read.csv("results/za_allometry_coefs.csv")

# Assign long bones as factors
us_coef$long_bone <- factor(us_coef$long_bone, 
                            levels=c("Humerus","Radius","Femur","Tibia"))
za_coef$long_bone <- factor(za_coef$long_bone, 
                            levels=c("Humerus","Radius","Femur","Tibia"))

# Plot U.S. data as point and line graph
us_plot <- ggplot(us_coef, aes(x=long_bone, y=slope, group=method)) + 
  geom_hline(yintercept=1, linetype="solid", size=0.5, col="red",alpha=0.5) + 
  geom_point(pch=1,size=3) + geom_line(aes(linetype=method), size=1) + 
  scale_y_continuous(limits=c(0.8,1.6),breaks=seq(0.8,1.6,0.2)) + 
  elaine_theme + scale_linetype_manual(values=c("solid","dashed","dotted",
                                                "dotdash","twodash")) +
  labs(x="Long Bone", y="Allometry Coefficient", title="a) U.S. Sample") + 
  theme(legend.position="none", plot.title=element_text(hjust=0))

# Plot Z.A. data as point and line graph
za_plot <- ggplot(za_coef, aes(x=long_bone, y=slope, group=method)) + 
  geom_hline(yintercept=1, linetype="solid", size=0.5, col="red",alpha=0.5) + 
  geom_point(pch=1,size=3) + geom_line(aes(linetype=method), size=1) + 
  scale_y_continuous(limits=c(0.8,1.6),breaks=seq(0.8,1.6,0.2)) + 
  elaine_theme + scale_linetype_manual(values=c("solid","dashed","dotted",
                                                "dotdash","twodash")) +
  labs(x="Long Bone", y="Allometry Coefficient", title="b) Z.A. Sample") + 
  theme(legend.position="none", plot.title=element_text(hjust=0))

# Arrange Plots Side-by-Side
grid.arrange(us_plot, za_plot, ncol=2)
```

## Figure 4
**Caption:** Bivariate relationship between stature (x) and alternative size variables (y) in log-normal space. The solid green line represents isometry. Note the magnitude and directionality of the black, non-solid line crossing the isometry line.

```{r Fig4}
# Import RMA coefficient results with slope and intercept
rma_results <- read.csv("results/rma_coefficients.csv")

# Import U.S. Log data
us_log <- readRDS("data/us_log.rds")

# Individual plot for RMSB v. Stature
rmsb_idx <- which(rma_results$size_var=="RMSB")  # index for RMSB
c_rmsb <- ggplot(us_log, aes(x=stature,y=RMSB)) + 
  geom_point(pch=1,col="grey") + 
  geom_abline(slope=1, 
              intercept=mean(us_log$RMSB)-mean(us_log$stature),
              size=1.15,col="#009E73") + 
  geom_abline(slope=rma_results$slope[rmsb_idx],
              intercept=rma_results$intercept[rmsb_idx],
              size=1.15,linetype="dashed") + 
  labs(x=expression(paste(italic(ln),"(Stature)")),
       y=expression(paste(italic(ln),"(RMSB)"))) + elaine_theme

# Individual plot for FMSB v. Stature
fmsb_idx <- which(rma_results$size_var=="FMSB")  # index for FMSB
c_fmsb <- ggplot(us_log, aes(x=stature,y=FMSB)) + 
  geom_point(pch=1,col="grey") + 
  geom_abline(slope=1,
              intercept=mean(us_log$FMSB)-mean(us_log$stature),
              size=1.15,col="#009E73") + 
  geom_abline(slope=rma_results$slope[fmsb_idx],
              intercept=rma_results$intercept[fmsb_idx],
              size=1.15,linetype="dotted") +
  labs(x=expression(paste(italic(ln),"(Stature)")),
       y=expression(paste(italic(ln),"(FMSB)"))) + elaine_theme

# Individual plot for GM_msb v. Stature
gm_msb_idx <- which(rma_results$size_var=="GM_msb")  # index for GM_msb 
c_gm_msb <- ggplot(us_log, aes(x=stature,y=GM_msb)) + 
  geom_point(pch=1,col="grey") + 
  geom_abline(slope=1,
              intercept=mean(us_log$GM_msb)-mean(us_log$stature),
              size=1.15,col="#009E73") + 
  geom_abline(slope=rma_results$slope[gm_msb_idx],
              intercept=rma_results$intercept[gm_msb_idx],
              size=1.15,linetype="dotdash") +
  labs(x=expression(paste(italic(ln),"(Stature)")),
       y=expression(paste(italic(ln),"(GM_Midshaft)"))) + elaine_theme

# Individual plot for GM_len v. Stature
gm_len_idx <- which(rma_results$size_var=="GM_len")  # index for GM_len
c_gm_len <- ggplot(us_log, aes(x=stature,y=GM_len)) + 
  geom_point(pch=1,col="grey") + 
  geom_abline(slope=1,
              intercept=mean(us_log$GM_len)-mean(us_log$stature),
              size=1.15,col="#009E73") + 
  geom_abline(slope=rma_results$slope[gm_len_idx],
              intercept=rma_results$intercept[gm_len_idx],
              size=1.15,linetype="twodash") +
  labs(x=expression(paste(italic(ln),"(Stature)")),
       y=expression(paste(italic(ln),"(GM_Length)"))) + elaine_theme

# Arrange plots as 2x2
grid.arrange(c_rmsb,c_fmsb,c_gm_msb,c_gm_len,nrow=2,
             layout_matrix=rbind(c(1,1,2,2),
                                 c(3,3,4,4)))
```

## Figure 5
**Caption:** Allometry coefficient relationships between long bone diaphyseal lengths from averaged coefficients from [Auerbach & Sylvester (2011)](https://onlinelibrary.wiley.com/doi/pdf/10.1002/ajpa.21418?casa_token=uBT2LwYVMWsAAAAA:ZwCvxoJ6r2NAj7OeNNYD2x11ZzzJllI2RlUo9ukCRIowyrkRkURsgBWABHb2tgMApsusAQHHA7--Tkc) on the left and the current study on the right. The solid red line across slope=1.0 represents isometry. Solid line = stature, dotted line = GM diaphyseal length.

```{r Fig5, fig.width=8, fig.height=4}
# Import U.S. and Auerbach & Sylvester coefficient data
us_coef <- read.csv("results/us_allometry_coefs.csv")
as_coef <- read.csv("data/Auerbach&Sylvester_2011.csv")

# Add study column
us_coef$study <- "Current Study"

# Combine data
comp_coef <- rbind(us_coef[which(us_coef$method %in% 
                                     c("Stature","GM_Length")),], as_coef)

# Define long bone as factor
comp_coef$long_bone <- factor(comp_coef$long_bone, 
                              levels=c("Humerus","Radius","Femur","Tibia"))

## Plot
ggplot(comp_coef, aes(x=long_bone, y=slope, group=method)) + 
  geom_hline(yintercept=1, linetype="solid", size=0.5, col="red", alpha=0.5) + 
  geom_line(aes(linetype=method), size=1) + geom_point(pch=1, size=3) + 
  scale_y_continuous(breaks=seq(0.8,1.6,by=0.2)) + 
  scale_linetype_manual(values=c("dotted","solid")) + 
  labs(x="Long Bone", y="Allometry Coefficient") + 
  facet_grid(cols=vars(study)) + elaine_theme + theme(legend.position="none") 
```

